An eight-year-long low-frequency earthquake catalog for Southern Cascadia

### 2022-01-26 paper/agujournaltemplate_highlighted.tex
Work on revisions

We then looked for LFEs during the period from July 2007 to June 2009, which correspond to the period when the FAME experiment was operating. Using a threshold equal to eight times the median absolute deviation of the stacked cross-correlation may produce false detections, therefore we filtered the LFE detection times before visualizing the two-year-long catalog. As the number of seismic stations recording may change with time as the stations were progressively installed during Summer and Fall 2007, and then progressively removed during May and June 2009, we kept only LFE detections for which the product of the \textbf{stacked} cross-correlation value by the number of \textbf{channels} recording at that time is higher than a threshold. \textbf{We will explain later in the text how the threshold is chosen}. The threshold is different for each LFE family, \textbf{but is constant over time for a given LFE family}. The resulting LFE catalog for the period 2007-2009 is shown in Figure 3. For comparison, we also plotted the tremor detection times from ~\citeA{BOY_2015}. \textbf{Filtering the catalog has removed about 84 \% of the LFEs. As a reference, we plotted in the Supplementary Material the catalog without filtering the LFEs and the number of channels recording as a function of time.} \\

@@

Once we have obtained a catalog for the period 2007-2009 using the data from the permanent seismic networks, we compare the LFE detections between the two catalogs: the FAME catalog (obtained with data from the FAME experiment) and the networks catalog (obtained from data from the permanent networks). As we may have many false detections, we try to eliminate some of them by assuming that LFEs present in both catalogs are always true detections. Then we define two thresholds: the first threshold is chosen such that at least half the LFE detections above the threshold in the FAME catalog are also in the network catalog, the second threshold is chosen such that at least half the LFE detections above the threshold in the network catalog are also in the FAME catalog. If we filter the catalogs and keep only detections above the thresholds, we are now confident that at least half of the LFE detections are true detections. As the number of stations recording may vary over time (especially for the network catalog), we keep only the LFE detections such that the associated cross correlation multiplied by the number of channels recording at that time is higher than the threshold. Thus, if there are few stations recordings at some time, the cross correlation must be higher for the LFE to be considered as a true detection. We then compared the normalized number of LFEs obtained with the two catalogs. Examples are given in Figure 5 for families A (square in Figure 1) and E (inverted triangle in Figure 1). Although the number of LFEs during each event may not be the same, we clearly see for family E that the timing of the events are the same for both catalogs. Family A has much shorter recurrence times but most events \textbf{are present in both catalogs as well: forty events are present in both catalogs, three events are present in the FAME catalog but not in the networks catalog and one event is present in the networks catalog but not in the FAME catalog.} \\

@@

For most of the families located on the subduction zone, we obtained a good agreement between both catalogs. We eliminate six families for which too few permanent stations have good templates, and it was not possible to detect LFEs with the available templates. However, we were able to detect most LFE events even without the presence of the temporary stations from the FAME network. We are thus confident that we can detect LFEs before 2007 and after 2009. In the following, we focus on the period 2004-2011. In November 2011, several one-component stations stopped recording and the number of available stations started decreasing, which is why we did not look for LFE events after that date. The resulting LFE catalog for the period 2004-2011 is shown in Figure 6. For comparison, we also plotted the tremor detection times from ~\citeA{BOY_2015}. Figure 7 shows the details of six big ETS events in 2004, 2005, 2006, 2007 and 2008. \textbf{The catalog shown in Figure 6 has been filtered using the threshold computed above. Filtering the catalog has removed about 63 \% of the LFEs. As a reference, we plotted in the Supplementary Material the catalog without filtering the LFEs and the number of channels recording as a function of time.} \\

>>>>

We then looked for LFEs during the period from July 2007 to June 2009, which correspond to the period when the FAME experiment was operating. Using a threshold equal to eight times the median absolute deviation of the stacked cross-correlation may produce false detections, therefore we filtered the LFE detection times before visualizing the two-year-long catalog. As the number of seismic stations recording may change with time as the stations were progressively installed during Summer and Fall 2007, and then progressively removed during May and June 2009, we kept only LFE detections for which the product of the \textbf{stacked} cross-correlation value by the number of \textbf{channels} recording at that time is higher than a threshold. \textbf{We will explain later in the text how the threshold is chosen}. The threshold is different for each LFE family, \textbf{but is constant over time for a given LFE family}. The resulting LFE catalog for the period 2007-2009 is shown in Figure 3. For comparison, we also plotted the tremor detection times from ~\citeA{BOY_2015}. \textbf{Filtering the catalog has removed about 84 \% of the LFEs, compared to the initial catalog where LFEs were detected using the 8 * MAD threshold for the cross-correlation. As a reference, we plotted in the Supplementary Material (Figure S1) the catalog without filtering the LFEs and the number of channels recording as a function of time.} \\

@@

Once we have obtained a catalog for the period 2007-2009 using the data from the permanent seismic networks, we compare the LFE detections between the two catalogs: the FAME catalog (obtained with data from the FAME experiment) and the networks catalog (obtained from data from the permanent networks). As we may have many false detections, we try to eliminate some of them by assuming that LFEs present in both catalogs are always true detections. Then we define two thresholds: the first threshold is chosen such that at least half the LFE detections above the threshold in the FAME catalog are also in the network catalog, the second threshold is chosen such that at least half the LFE detections above the threshold in the network catalog are also in the FAME catalog. If we filter the catalogs and keep only detections above the thresholds, we are now confident that at least half of the LFE detections are true detections. As the number of stations recording may vary over time (especially for the permanent networks catalog), we keep only the LFE detections such that the associated cross correlation multiplied by the number of channels recording at that time is higher than the threshold. Thus, if there are few stations recordings at some time, the cross correlation must be higher for the LFE to be considered as a true detection. We then compared the normalized number of LFEs obtained with the two catalogs. Examples are given in Figure 5 for families A (square in Figure 1) and E (inverted triangle in Figure 1). Although the number of LFEs during each \textbf{cluster of LFEs} may not be the same, we clearly see for family E that the timing of the events are the same for both catalogs. Family A has much shorter recurrence times but most \textbf{clusters of LFEs are present in both catalogs as well: forty clusters are present in both catalogs, three clusters are present in the FAME catalog but not in the networks catalog and one cluster is present in the networks catalog but not in the FAME catalog.} \\

@@

For most of the families located on the subduction zone, we obtained a good agreement between both catalogs. We eliminate six families for which too few permanent stations have good templates, and it was not possible to detect LFEs with the available templates. However, we were able to detect most LFE events even without the presence of the temporary stations from the FAME network. We are thus confident that we can detect LFEs before 2007 and after 2009. In the following, we focus on the period 2004-2011. In November 2011, several one-component stations stopped recording and the number of available stations started decreasing, which is why we did not look for LFE events after that date. The resulting LFE catalog for the period 2004-2011 is shown in Figure 6. For comparison, we also plotted the tremor detection times from ~\citeA{BOY_2015}. Figure 7 shows the details of six big ETS events in 2004, 2005, 2006, 2007 and 2008. \textbf{The catalog shown in Figure 6 has been filtered using the threshold computed above. Filtering the catalog has removed about 63 \% of the LFEs, compared to the initial catalog where LFEs were detected using the 8 * MAD threshold for the cross-correlation. As a reference, we plotted in the Supplementary Material (Figure S2) the catalog without filtering the LFEs and the number of channels recording as a function of time.} \\
